MCC Informativeness - moving agent pilots kids

### 2018-08-08 stats/mcc_inf_pilot_kids.Rmd
new pilot of inforamtiveness and new version of novelty, both kids

## importing data
d <- inf.data %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

@@

>>>>

## importing data
d2 <- inf.data %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(age) %>%
  summarise(n = length(unique(subid))) %>%
  knitr::kable(digits = 3)

d2 %>%
  group_by(age) %>%
  summarise(n = length(unique(subid))) %>%
  knitr::kable(digits = 3)

@@

```{r plot}

p <- d2 %>%
  filter(trial_type == "test") %>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

### 2018-08-08 stats/mcc_novel_pilot_kids.Rmd
new pilot of inforamtiveness and new version of novelty, both kids

## importing data
d <- inf.data %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

@@

p <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

>>>>

## importing data
d <- novel.data %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
  filter(trial != "7", trial != "8")

@@

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(age,change,trial_type) %>%
  summarise(n = length(unique(subid)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

@@

p <- d %>%
  filter(trial != "train") %>%
  group_by(change, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .01)+
  geom_pointrange(data = p1, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```
